---
title: "inspect"
author: "Konner Macias"
date: "May 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data
```{r}
perGame <- read.csv("../data/player-data-wrangled/player2015/PerGame-2015wrangled.csv", stringsAsFactors = FALSE)
advStats <- read.csv("../data/player-data-wrangled/player2015/Adv-2015wrangled.csv", stringsAsFactors = FALSE)
```
Merge the data frames
```{r}
pgAdv <- merge(perGame, advStats, by = c("Player","Pos","G","Tm","Age","fix"))
pgAdv <- pgAdv[-c(7,8,33,34,48,53)]
colnames(pgAdv)
```
```{r}
summary(pgAdv)
```

# Get FA Player data
```{r}
fAgents <- read.csv('../data/salary-data/fixed-fa-signings/fixed-2015.csv', stringsAsFactors = FALSE)
fAgents <- fAgents[-c(1,2,3,4,5,6,7)]
colnames(fAgents)
```

# Get other players
```{r}
playerFixed <- read.csv('../data/salary-data/fixed-average-salaries/fixed-2015.csv', stringsAsFactors = FALSE)
playerFixed <- playerFixed[-c(1,3,4,5,6)]
colnames(playerFixed)
```
```{r}
mega2 <- merge(pgAdv, playerFixed, by.x = "fix", by.y = "name")
mega2[is.na(mega2)] <- 0
write.csv(mega2, "mega2.csv")
colnames(mega2)
```


```{r}
mega <- merge(pgAdv, playerFixed[-c(1)], by.x = "fix", by.y = "name")
mega[is.na(mega)] <- 0
colnames(mega)
write.csv(mega, "mega.csv")
```


```{r}
library(ggplot2)
library(GGally)
library(corrplot)
M <- cor(mega[-c(1,2,3,5)])
corrplot(M,method = "circle", type = "upper")
```
# Noteworthy variables:
GS, MP.x, FG, FGA, X2P, X2PA, FT, FTA, ORB, DRB, TRB, AST, STL, TOV, PF, PS.G, MP.y, PER, USG., OWS, DWS, WS, OBPM, BPM, VORP, average.salary
# Let's look at only those
```{r}
M <- cor(mega[c(7,8,9,10,15,16,19,20,22,23,24,25,26,28,29,30,31,32,43,44,45,46,48,50,51,52)])
corrplot.mixed(M, lower = "number", upper = "circle")
```


```{r}
sort(M[26,],decreasing = TRUE)
```
Let's look at FG first
```{r}
sort(M[3,],decreasing = FALSE)
```
Now WS
```{r}
sort(M[22,],decreasing = FALSE)
```
Now TOV
```{r}
sort(M[14,],decreasing = FALSE)
```


# Now Create Linear Models

```{r}
library(car)
m1 <- lm(average.salary ~ FG + WS + TOV + DRB + MP.y, data=mega)
summary(m1)
vif(m1)
```
```{r}
par(mfrow=c(2,2))
plot(m1)
```


```{r}
redMega <- mega[c(7,8,9,10,15,16,19,20,22,23,24,25,26,28,29,30,31,32,43,44,45,46,48,50,51,52)]
colnames(redMega)
```
# How do these reduced variables correlate with each other?
```{r}
ggpairs(redMega[c(3,4,10,14,16,17,22,25,26)])
```

# Let's find subset that gives highest R^2
```{r}
library(leaps)
bm <- regsubsets(average.salary ~ GS + MP.x + FG + FGA + X2P + X2PA + FT + FTA + ORB + DRB + TRB + AST + STL + TOV + PF + PS.G + MP.y + PER + USG. + OWS + DWS + WS + OBPM + BPM + VORP, data = redMega, nbest=1, nvmax=NULL, force.in=NULL, force.out=NULL,method="exhaustive")
bm.sum <- summary(bm)
res.legend <-subsets(bm, statistic="adjr2", legend = FALSE, min.size = 3, max.size = 12, main = "Adjusted R^2")
```

```{r}
which.max(bm.sum$adjr2)
```

# Igsignificant variables, we want to generalize better. Don't want to overfit!

```{r}
bm.sum$which[10,]
```
```{r}
m10 <- lm(average.salary ~ FGA + FT + DRB + AST + TOV + PF + MP.y + PER + OWS + BPM, data = redMega)
summary(m10)
vif(m10)
```
# Good R^2, but bad VIF for TOV
## VIF = variance inflation factor (checks for collinearity)
```{r}
bm.sum$which[9,]
```

```{r}
m9 <- lm(average.salary ~ FG + DRB + AST + TOV + PF + MP.y + PER + WS + OBPM, data = redMega)
summary(m9)
vif(m9)
```
# Still bad VIF
```{r}
bm.sum$which[8,]
```
```{r}
m8 <- lm(average.salary ~ FG + DRB + TOV + PF + MP.y + PER + WS + OBPM, data = redMega)
summary(m8)
vif(m8)
```
This is the best model!
```{r}
par(mfrow=c(2,2))
plot(m8)
```


```{r}
 plot(density(redMega$average.salary,bw="SJ",kern="gaussian"),type="l",main="Gaussian
kernel density estimate",xlab="Average Salary")
```

```{r}
qqnorm(redMega$average.salary, ylab = "Average Salary")
qqline(redMega$average.salary, lty = 2, col = 2)
```

Seems to be light-tailed. Let's use a Log transformation
```{r}
qqnorm(log(redMega$average.salary), ylab = "Average Salary")
qqline(log(redMega$average.salary), lty = 2, col = 2)
```
```{r}
qqnorm(I(redMega$average.salary)^0.33, ylab = "Average Salary")
#qqline(I(redMega$average.salary)^0.33, lty = 2, col = 2)
```
```{r}
qqnorm(sqrt(redMega$average.salary), ylab = "Average Salar")
qqline(sqrt(redMega$average.salary), lty = 2, col = 2)
```


# FREE AGENTS ONLY
# Merge into final data frame
```{r}
megaFreeAgents <- merge(pgAdv, fAgents, by.x = "fix", by.y ="name")
megaFreeAgents[is.na(megaFreeAgents)] <- 0
write.csv(megaFreeAgents, file = "mega.csv")
megaFreeAgents <- megaFreeAgents[-c(1,2,3,5)]
colnames(megaFreeAgents)
```

# Now let's look at only those
```{r}
M <- cor(mega[c(3,4,5,6,7,11,12,15,16,18,19,20,22,26,27,40,41,42,46,47,49)])
corrplot.mixed(M, lower = "number", upper = "circle")
```


